
%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the TDPTemplate using
% the LaTeX document class 'llncs.cls' Springer LNAI format
% used in the RoboCup Symposium submissions.
% http://www.springer.com/computer/lncs?SGWID=0-164-6-793341-0
%
% It may be used as a template for your own TDP - copy it
% to a new file with a new name and use it as the basis
% for your Team Description Paper
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

% document input
\usepackage[utf8]{inputenc}		% input encoding
\usepackage[english]{babel}		% input language for hyphens

% fonts 
\usepackage[T1]{fontenc}		% more glyphs and a
\usepackage{lmodern}			% better looking font

% page geometry
%\usepackage{a4wide}
%\usepackage{a4}
%\usepackage[left=48mm,right=46mm]{geometry}
\usepackage[left=32mm,right=31mm]{geometry}

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}

\usepackage{graphicx}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{float}
\usepackage{boxedminipage}

\usepackage{url}
\usepackage{hyperref}
\usepackage{listings}

\usepackage{ctex}
\usepackage{setspace}
 \usepackage{graphicx} 
 \usepackage{subfigure}
 
\renewcommand{\baselinestretch}{1}


% *** MORE GRAHPICS ***
\usepackage[usenames,dvipsnames]{color}     

% *** BIBLIOGRAPHY PACKAGES ***
%\usepackage{natbib}     

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{booktabs}           % For tables (toprule, midrule, bottomrule)
\usepackage{todonotes}			% should be defined after the color package
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% *** PATHS ***
\makeatletter
\def\input@path{{images/}		
				}
\makeatother

\graphicspath{  {images/}
				}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Acronym definitions
\usepackage[acronym]{glossaries}
\newacronym{ed}{ED}{Environment Descriptor}
\newacronym{gui}{GUI}{Graphical User Interface}
\newacronym{fcfg}{FCFG}{feature context free grammar}

% shorthand definitions
\newcommand{\eg}{\emph{e.g.}}						% Exemplum gratia
\newcommand{\goal}{\mathcal{G}}						% Goal area
\newcommand{\goallc}{\mathcal{G}_{\mathrm{lc}}}		% Subset of goal area with costs below threshold cmin
\newcommand{\goalhc}{\mathcal{G}_{\mathrm{hc}}}		% Subset of goal area with costs above threshold cmin
\newcommand{\ie}{\emph{i.e.}}						% Id est
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




\begin{document}
	
\title{Tinker@Home 2019 Team Description Paper}
\author{Jianghao Huo, Xinyu Han, Junda Bi, Haocheng Ma, Renjie Ma, Cuijie Xu, Lubin Ye, Han Zhang, Tengfei Zhang, Zijian Zhang and Yao Jiang}
\institute{Future Robotics Club(Group), Tsinghua University,  China\\
\texttt{Homepage: http://tinker.furoc.net} \\
\texttt{Email: jiangyaonju@126.com} \\
\texttt{Correspondence: robocup-tinker@googlegroups.com}}
\authorrunning{J Huo et al.}	
\maketitle

\begin{abstract}
This paper describes an intelligent robot named Tinker of Tsinghua University, China, including the mechanical system, hardware system and software system. Tinker is designed to be an autonomous robot in domestic environment, capable of navigating and manipulating in complicated environment with friendly interaction interface, aiming to accomplish the tasks of @Home League of World RoboCup 2019. This paper gives the hardware and software design we have proposed and implemented.
\end{abstract}

\section{Introduction}
Automatic home service is a research hotspot these years, which calls for a more intelligent and reliable robot. With the best interest in robot, Tinker is created by FuRoC team (Future Robotics Club), a student club from Tsinghua University focusing on robotics, AI and related fields. Robocup@HOME 2019 is our forth participation in the @home League of World RoboCup. Tinker is designed to be an autonomous humanoid robot mainly for home service. The capability such as automatic navigation, environment perception, interaction with human, vision recognizing and objects carrying, etc, are necessary. Tinker is equipped with a agile mobile chassis using 4 mecanum wheels, a UR5 robotic arm ,a powerful  mechanical gripper (Robotiq-G85), and various types of sensor. Depth cameras (Kinect v2 and realsense d435i) are used for imaging and recognizing environment, objects and people. 2 laser range-finders and 1 3D Lidar are used for environment perception and obstacle avoidance. To confirm the objects grabbing, the gripper is equipped with a Laser transmitter and receiver sensor.

\section{Overview of the robot}
\input{arch.tex}

\section{Mechanical Design}
\input{mec.tex}

\section{Software Engineering}
\subsection{Computer Vision}
Computer vision is indispensable for tinker to accomplish multiple tasks including person recognition, object manipulation and environment modeling.
\input{vision.tex}

\subsection{Navigation}
\input{nav.tex}

\subsection{Speech Recognition}
\input{speech.tex}


\section{Team repository}
Our team repository can be found at \url{https://github.com/tinkerfuroc}. The repository may be of help to other teams by providing:
\begin{enumerate}
    \item Implementation of all the algorithms and needed parameters described in the paper
    \item Robot setup scripts and tools
    \item Code for RoboCup@Home tasks 
\end{enumerate}

\section{3rd Party Dependencies}
\begin{enumerate}
    \item \href{www.ros.org}{ROS}
    \item \href{github.com/ros-planning/navigation}{ROS Navigation Stack}
    \item \href{github.com/code-iai/iai\_kinect2}{iai\_kinect2}
    \item \href{github.com/pjreddie/darknet}{darknet(tensorflow fast yolo)}
    \item \href{www.tensorflow.org}{tensorflow}
    \item \href{www.faceplusplus.com}{face++}
\end{enumerate}


%As Tinker is young, there are still a lot of things to learn and improve.

%Citation test \cite{xia2015human}.

\section*{Acknowledgement}
The authors of this paper would like to thank previous team members of Tinker@Home 2014, Tinker@Home2015, Tinker@Home2017 for their help and support through out building the robot and writing this manuscript. The authors would also like to thank Face++, dorabot, Questyle Audio, and Mech-Mind, for their material or technology support. 


\bibliography{main.bib}
\bibliographystyle{IEEEtran}


\end{document}
